---
title: "p8105_hw1_yl5839"
author: "Yuying Lu"
date: "2024-09-15"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Problem 1

**Data Importing**

```{r}
data("penguins",package="palmerpenguins")
penguins
```

```{r}
summary(penguins)
```


**Description**

The `penguins` dataset has `r nrow(penguins)` rows and each row vector includes the information of a collected penguin sample. Meanwhile, there are `r ncol(penguins)` columns in the dataset, representing different characteristics of the penguins. The columns are `r colnames(penguins)``, which respectively refer to the species, island, bill length, bill depth, flipper length, body mass sex and the study year of each collected sample.

The study years of these samples are `r factor(unique(penguins$year))`. There are three species penguins (`r unique(penguins$species)`) included in this dataset and they come from three islands (`r unique(penguins$island)`). 

Regardless of some missing data, the dataset contains `r sum(penguins$sex=='female',na.rm = TRUE)` female penguins and `r sum(penguins$sex=='male',na.rm = TRUE)` male penguins. The mean values of other four variables are listed as below: 

| bill length(mm) | bill depth(mm) | flipper length(mm) | body mass(g)|
|:---:|:---:|:---:|:---:|
|`r round(mean(penguins$bill_length_mm,na.rm=TRUE),2)`| `r round(mean(penguins$bill_depth_mm,na.rm=TRUE),2)`|`r round(mean(penguins$flipper_length_mm,na.rm=TRUE),2)`| `r round(mean(penguins$body_mass_g,na.rm=TRUE),2)`|


**Plotting**

Use `ggplot()` to create a scatterplot of `flipper_length_mm` (y) vs `bill_length_mm` (x).
```{r,message=FALSE,warning=FALSE, fig.width=8,fig.height==12}
library(tidyverse)
ggplot(penguins,aes(x=bill_length_mm,y=flipper_length_mm,color=species))+
  geom_point(alpha=.5)
```


Export the scatterplot.

```{r,message=FALSE,warning=FALSE,fig.width=8,fig.height=12}
ggsave('flipper_length_vs_bill_length.png')
```

# Problem 2

```{r}
set.seed(111)
df<-tibble(vec_sample=rnorm(10),
           vec_logic=vec_sample>0,
           vec_char=c('A','B','C','E','F','11','12','D','133','S'),
           vec_factor=factor(c('black','white','red','red','black','black','white','red','white','white'),levels=c('black','white','red')))
df
```
**Try to Take the Mean**

- The mean of `vec_sample` is `r mean(pull(df,vec_sample))`;
- The mean of `vec_logic` is `r mean(pull(df,vec_logic))`;
- The mean of `vec_char` is `r mean(pull(df,vec_char))`;
- The mean of `vec_factor` is `r mean(pull(df,vec_factor))`;


As shown above, the function `mean()` works on the numeric variable `vec_sample` and the logical variable `vec_logic`. However, it doesn't work on the character variable `vec_char` and factor variable `vec_factor`. 

**Try Function `as.numeric`**

When I try `as.numeric()` function to the logical, character, and factor variables using the following code:
```{r eval=FALSE}
as.numeric(pull(df,vec_logic))
as.numeric(pull(df,vec_char))
as.numeric(pull(df,vec_factor))
```

- For logical variable, it converts 'TRUE' to 1 and converts 'FALSE' to 0;
- For character variable, it turns a non-numeric character like 'A' to NA and turns a numeric character like '12' to the number itself;
- For factor variable, it returns the integer inherited the priority of the factor levels. In our example, the integer be assigned to 'black','white' and 'red', are 1,2 3 respectively, because the level of factor is 'black','white', 'red'.


There is a possible explanation for the results of applying `mean()` to these three types of variables. When I apply function `mean()` to a logical, it will automatically regard the logical variable `vec_logic` as the numeric number `as.numeric(vec_logic)`. However, when applying function `mean()` to the character variable or the factor variable, it can't actually turn them to a numeric number. Therefore, it results to NA when taking the mean of character variable or the factor variable using `mean()`.

