---
title: "p8105_hw1_yl5839"
author: "Yuying Lu"
date: "2024-09-15"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Problem 1

**Data Importing**

```{r}
data("penguins",package="palmerpenguins")
penguins
```

```{r}
summary(penguins)
```


**Description**

The `penguins` dataset has `r nrow(penguins)` rows and each row vector includes the information of a collected penguin sample. Meanwhile, there are `r ncol(penguins)` columns in the dataset, representing different characteristics of the penguins. The columns are `r colnames(penguins)``, which respectively refer to the species, island, bill length, bill depth, flipper length, body mass sex and the study year of each collected sample.

The study years of these samples are `r factor(unique(penguins$year))`. There are three species penguins (`r unique(penguins$species)`) included in this dataset and they come from three islands (`r unique(penguins$island)`). 

Regardless of some missing data, the dataset contains `r sum(penguins$sex=='female',na.rm = TRUE)` female penguins and `r sum(penguins$sex=='male',na.rm = TRUE)` male penguins. The mean of the rest four variables are listed as below: 

| bill length(mm) | bill depth(mm) | flipper length(mm) | body mass(g)|
|:---:|:---:|:---:|:---:|
|`r round(mean(penguins$bill_length_mm,na.rm=TRUE),2)`| `r round(mean(penguins$bill_depth_mm,na.rm=TRUE),2)`|`r round(mean(penguins$flipper_length_mm,na.rm=TRUE),2)`| `r round(mean(penguins$body_mass_g,na.rm=TRUE),2)`|




```{r,message=FALSE,warning=FALSE}
# load a necessary package
library(tidyverse)
ggplot(penguins,aes(x=bill_length_mm,y=flipper_length_mm,color=species))+
  geom_point(alpha=.5)
ggsave('flipper_length_vs_bill_length.png')
```
